---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tadaathemes

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/tadaadata/tadaathemes/workflows/R-CMD-check/badge.svg)](https://github.com/tadaadata/tadaathemes/actions)
[![CRAN status](https://www.r-pkg.org/badges/version/tadaathemes)](https://CRAN.R-project.org/package=tadaathemes)
<!-- badges: end -->

The goal of tadaathemes is to provide a bunch of reasonably neat ggplot2 themes.

## Installation

~~You can install the released version of tadaathemes from [CRAN](https://CRAN.R-project.org) with~~:

``` r
# install.packages("tadaathemes")
```

## Examples

Include a (compact?) gallery of themes (or maybe move them to a dedicated pkgdown article)

```{r example}
# library(tadaathemes)
```


## Additional Resources

- [r-graph-gallery.com](https://www.r-graph-gallery.com/): For inspiration.
- [calligross/ggthemeassist](https://github.com/calligross/ggthemeassist): RStudio addin for interactive theme tweaking.
- [metrumresearchgroup/ggedit](https://github.com/metrumresearchgroup/ggedit): Another RStudio addin
- [wilkelab/cowplot](https://github.com/wilkelab/cowplot): Just generally useful.

### Themes / Theming

- [hrbrmstr/hrbrthemes](https://github.com/hrbrmstr/hrbrthemes): For the *good stuff*.
- [hrbrmstr/ggexpanse](https://github.com/hrbrmstr/ggexpanse): Everyone needs more The Expanse.
- [cttobin/ggthemr](https://github.com/cttobin/ggthemr): 
- [delabj/ggCyberPunk](https://github.com/delabj/ggCyberPunk): For the cyberpunk aesthetic.
- [briandconnelly/lato](https://github.com/briandconnelly/lato): Simple themes with Lato font.
- [nanxstats/ggsci](https://github.com/nanxstats/ggsci): For looking sciency.
- [nsgrantham/ggdark](https://github.com/nsgrantham/ggdark): Dark version of ggplot2 default themes.
- [datarootsio/artyfarty](https://github.com/datarootsio/artyfarty): Unmaintained, but good for inspiration I guess.
- [schochastics/Rokemon](https://github.com/schochastics/Rokemon): Pokémon themes.
- [Ryo-N7/tvthemes](https://github.com/Ryo-N7/tvthemes): TV show themes.
- [moldach/vapoRwave](https://github.com/moldach/vapoRwave): Everything is better with some ＶＡＰＯＲＷＡＶＥ
- [xkcd](https://github.com/cran/xkcd): Because of course.


### Colors

- [sjmgarnier/viridisLite](https://github.com/sjmgarnier/viridisLite): Viridis is the (at least my) preferred set of color scales for continuous variables
- [coolors](https://coolors.co/): Make your own color palettes easily (up to 5, therefore only useful for qualitative palettes etc.).

### Plotting *with fonts* (and text stuff)

- [wilkelab/ggtext](https://github.com/wilkelab/ggtext): Markdown text formatting in ggplot2! (WIP)
- [r-lib/ragg](https://github.com/r-lib/ragg/): Alternative output device which, among general performance/quality improvements, also eases the inclusion of system fonts.
- [rstudio/thematic](https://github.com/rstudio/thematic/) (WIP): Auto-theming depending on context, easy styling using [rstudio/bootstraplib](https://github.com/rstudio/bootstraplib) in RMarkdown/shiny/RStudio(!). The latter is also WIP.
- [yixuan/showtext](https://github.com/yixuan/showtext): For plotting with fonts, including the easy inclusion of Google fonts.
- [wch/extrafont](https://github.com/wch/extrafont): Probably maybe required to use fonts for PDF output (using `cairo_pdf`)? I still don't quite understand it, but `extrafont::loadfonts()` tends to do more good than harm.

### Reading

- [Thread (with links) about dark themes and readability](https://twitter.com/jburnmurdoch/status/1231235791562694659)
    - https://uxmovement.com/content/why-you-should-never-use-pure-black-for-text-or-backgrounds/
    - https://markboulton.co.uk/journal/five-simple-steps-to-better-typography/
    - https://schlosslab.discovery.wisc.edu/wp-content/uploads/2018/09/SchlossGramazioSilvermanParkerWanginPress.pdf
    - https://www.nngroup.com/articles/dark-mode/
